
---
output:
  md_document:
    variant: markdown_github
---

#quicknews: r package for quick/multi-lingual web-based corpus creation

facilitates quick/easy web scraping of news sources, as a dataframe in text interchange format...

The two web-based functions presented here more or less work in tandem. Both functions depend on functionality made available in the `boilerpipeR`, `XML`, and `RCurl` packages. 

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(quicknews)#devtools::install_github("jaytimm/quicknews")
library(DT)
```


###qnews_get_meta()

`qnews_get_meta` simply pulls metadata based on user-specified search paramaters from the GoogleNews RSS feed.  Here, we search for US-based business-related articles written in Spanish.

```{r}
es_us_business_meta <- quicknews::qnews_get_meta  (language="es", country="us", type="topic", search='business')
```

Metadata include:
```{r echo=FALSE}
colnames(es_us_business_meta)
```

First six article titles:
```{r}
es_us_business_meta%>%
  select(date:title)
```


###qnews_scrape_web()

The second web-based function, `qnews_scrape_web`, scrapes text from the web addresses included in the output from `qnews_get_meta`.  The function returns a [TIF](https://github.com/ropensci/tif#text-interchange-formats)-compliant dataframe, with each scraped text represented as a single row.  Metadata from output of `qnews_get_meta` are also included.

```{r}
es_us_business_corpus <- es_us_business_meta%>% 
  quicknews::qnews_scrape_web (link_var='link')
```


